moderated_regressions

### 2024-04-30 moderated_regressions.Rmd
updating tables

challenge_resource_burnout_model1 <- lm(burnout ~ overall.challenge_center, data = data)
summary(challenge_resource_burnout_model1)

challenge_resource_burnout_model2 <- lm(burnout ~ overall.challenge_center + overall.resource, data = data)
summary(challenge_resource_burnout_model2)

challenge_resource_burnout_model3 <- lm(burnout ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
summary(challenge_resource_burnout_model3)

aov_test <- anova(challenge_resource_burnout_model2, challenge_resource_burnout_model3)
```

@@

challenge_resource_stress_model1 <- lm(stress ~ overall.challenge_center, data = data)
summary(challenge_resource_stress_model1)

challenge_resource_stress_model2 <- lm(stress ~ overall.challenge_center + overall.resource_center, data = data)
summary(challenge_resource_stress_model2)

challenge_resource_stress_model3 <- lm(stress ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
summary(challenge_resource_stress_model3)

anova(challenge_resource_stress_model2, challenge_resource_stress_model3)
```

@@

challenge_resource_engagement_model1 <- lm(engagement ~ overall.challenge_center, data = data)
summary(challenge_resource_engagement_model1)

challenge_resource_engagement_model2 <- lm(engagement ~ overall.challenge_center + overall.resource_center, data = data)
summary(challenge_resource_engagement_model2)

challenge_resource_engagement_model3 <- lm(engagement ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
summary(challenge_resource_engagement_model3)

anova(challenge_resource_engagement_model2, challenge_resource_engagement_model3)
```

@@

hindrance_resource_model1 <- lm(burnout ~ overall.hindrance_center, data = data)
summary(hindrance_resource_model1)

hindrance_resource_burnout_model2 <- lm(burnout ~ overall.hindrance_center + overall.resource_center, data = data)
summary(hindrance_resource_burnout_model2)

hindrance_resource_burnout_model3 <- lm(burnout ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
summary(hindrance_resource_burnout_model3)

anova(hindrance_resource_burnout_model2, hindrance_resource_burnout_model3)
```

@@

hindrance_resource_stress_model1 <- lm(stress ~ overall.hindrance_center, data = data)
summary(hindrance_resource_stress_model1)

hindrance_resource_stress_model2 <- lm(stress ~ overall.hindrance_center + overall.resource_center, data = data)
summary(hindrance_resource_stress_model2)

hindrance_resource_stress_model3 <- lm(stress ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
summary(hindrance_resource_stress_model3)

anova(hindrance_resource_stress_model2, hindrance_resource_stress_model3)
```

@@

hindrance_resource_engagement_model1 <- lm(engagement ~ overall.hindrance_center, data = data)
summary(hindrance_resource_engagement_model1)

hindrance_resource_engagement_model2 <- lm(engagement ~ overall.hindrance_center + overall.resource_center, data = data)
summary(hindrance_resource_engagement_model2)

hindrance_resource_engagement_model3 <- lm(engagement ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
summary(hindrance_resource_engagement_model3)

anova(hindrance_resource_engagement_model2, hindrance_resource_engagement_model3)
```

```{r Numbers for Tables}

@@

# b weights
chal.2.burn <- round(summary(challenge_resource_burnout_model2)$coefficients[2, 1],6)
res.2.burn <- round(summary(challenge_resource_burnout_model2)$coefficients[3, 1],6)

int.3.burn <- round(summary(challenge_resource_burnout_model3)$coefficients[4, 1],6)

#r squared
challenge_resource_burnout_model2_r <- round(summary(challenge_resource_burnout_model2)$r.squared,4)
challenge_resource_burnout_model3_r <- round(summary(challenge_resource_burnout_model3)$r.squared,4)

## R square change
challenge_resource_burnout_anova <- anova(challenge_resource_burnout_model2, challenge_resource_burnout_model3)
challenge_resource_burnout_r_square_change <- round(challenge_resource_burnout_model3_r - challenge_resource_burnout_model2_r,4)

@@

DV <- c("Burnout","","")
Step <- c("1", "","2")
Model <- c("Challenge", "Resource", "Challenge X Resource")
b <- c(chal.2.burn,res.2.burn,int.3.burn)
DeltaR <- c("",paste(challenge_resource_burnout_model2_r,"**"),challenge_resource_burnout_r_square_change)

@@

>>>>

cr_burn_m1 <- lm(burnout ~ overall.challenge_center, data = data)
summary(cr_burn_m1)

cr_burn_m2 <- lm(burnout ~ overall.challenge_center + overall.resource, data = data)
summary(cr_burn_m2)

cr_burn_m3 <- lm(burnout ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
summary(cr_burn_m3)

aov_test <- anova(cr_burn_m2, cr_burn_m3)
```

@@

cr_stress_m1 <- lm(stress ~ overall.challenge_center, data = data)
summary(cr_stress_m1)

cr_stress_m2 <- lm(stress ~ overall.challenge_center + overall.resource_center, data = data)
summary(cr_stress_m2)

cr_stress_m3 <- lm(stress ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
summary(cr_stress_m3)

anova(cr_stress_m2, cr_stress_m3)
```

@@

cr_eng_m1 <- lm(engagement ~ overall.challenge_center, data = data)
summary(cr_eng_m1)

cr_eng_m2 <- lm(engagement ~ overall.challenge_center + overall.resource_center, data = data)
summary(cr_eng_m2)

cr_eng_m3 <- lm(engagement ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
summary(cr_eng_m3)

anova(cr_eng_m2, cr_eng_m3)
```

@@

hr_burn_m1 <- lm(burnout ~ overall.hindrance_center, data = data)
summary(hr_burn_m1)

hr_burn_m2 <- lm(burnout ~ overall.hindrance_center + overall.resource_center, data = data)
summary(hr_burn_m2)

hr_burn_m3 <- lm(burnout ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
summary(hr_burn_m3)

anova(hr_burn_m2, hr_burn_m3)
```

@@

hr_stress_m1 <- lm(stress ~ overall.hindrance_center, data = data)
summary(hr_stress_m1)

hr_stress_m2 <- lm(stress ~ overall.hindrance_center + overall.resource_center, data = data)
summary(hr_stress_m2)

hr_stress_m3 <- lm(stress ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
summary(hr_stress_m3)

anova(hr_stress_m2, hr_stress_m3)
```

@@

hr_eng_m1 <- lm(engagement ~ overall.hindrance_center, data = data)
summary(hr_eng_m1)

hr_eng_m2 <- lm(engagement ~ overall.hindrance_center + overall.resource_center, data = data)
summary(hr_eng_m2)

hr_eng_m3 <- lm(engagement ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
summary(hr_eng_m3)

anova(hr_eng_m2, hr_eng_m3)
```

```{r Numbers for Table1}

@@

#Challenge-Resource-Burnout

# b weights
chal.2.burn <- round(summary(cr_burn_m2)$coefficients[2, 1],2)
res.2.burn <- round(summary(cr_burn_m2)$coefficients[3, 1],2)

int.cr.3.burn <- round(summary(cr_burn_m3)$coefficients[4, 1],2)

#r squared
cr_burn_m2_r <- round(summary(cr_burn_m2)$r.squared,2)
cr_burn_m3_r <- round(summary(cr_burn_m3)$r.squared,2)

## R square change
cr_burn_anova <- anova(cr_burn_m2, cr_burn_m3)
cr_burn_r_square_change <- round(cr_burn_m3_r - cr_burn_m2_r,2)

#Challenge-Resource-Stress

# b weights
chal.2.stress <- round(summary(cr_stress_m2)$coefficients[2, 1],2)
res.2.stress <- round(summary(cr_stress_m2)$coefficients[3, 1],2)

int.cr.3.stress <- round(summary(cr_stress_m3)$coefficients[4, 1],2)

#r squared
cr_stress_m2_r <- round(summary(cr_stress_m2)$r.squared,2)
cr_stress_m3_r <- round(summary(cr_stress_m3)$r.squared,2)

## R square change
cr_stress_anova <- anova(cr_stress_m2, cr_stress_m3)
cr_stress_r_square_change <- round(cr_stress_m3_r - cr_stress_m2_r,2)

#Challenge-Resource-Engagement

# b weights
chal.2.eng <- round(summary(cr_eng_m2)$coefficients[2, 1],2)
res.2.eng <- round(summary(cr_eng_m2)$coefficients[3, 1],2)

int.cr.3.eng <- round(summary(cr_eng_m3)$coefficients[4, 1],2)

#r squared
cr_eng_m2_r <- round(summary(cr_eng_m2)$r.squared,2)
cr_eng_m3_r <- round(summary(cr_eng_m3)$r.squared,2)

## R square change
cr_eng_anova <- anova(cr_eng_m2, cr_eng_m3)
cr_eng_r_square_change <- round(cr_eng_m3_r - cr_eng_m2_r,2)
```

```{r Numbers for Table2}

#Hindrance-Resource-Burnout

# b weights
hind.2.burn <- round(summary(hr_burn_m2)$coefficients[2, 1],2)
res.2hr.burn <- round(summary(hr_burn_m2)$coefficients[3, 1],2)

int.hr.3.burn <- round(summary(hr_burn_m3)$coefficients[4, 1],2)

#r squared
hr_burn_m2_r <- round(summary(hr_burn_m2)$r.squared,2)
hr_burn_m3_r <- round(summary(hr_burn_m3)$r.squared,2)

## R square change
hr_burn_anova <- anova(hr_burn_m2, hr_burn_m3)
hr_burn_r_square_change <- round(hr_burn_m3_r - hr_burn_m2_r,2)

#Hindrance-Resource-Stress

# b weights
hind.2.stress <- round(summary(hr_stress_m2)$coefficients[2, 1],2)
res.2hr.stress <- round(summary(hr_stress_m2)$coefficients[3, 1],2)

int.hr.3.stress <- round(summary(hr_stress_m3)$coefficients[4, 1],2)

#r squared
hr_stress_m2_r <- round(summary(hr_stress_m2)$r.squared,2)
hr_stress_m3_r <- round(summary(hr_stress_m3)$r.squared,2)

## R square change
hr_stress_anova <- anova(hr_stress_m2, hr_stress_m3)
hr_stress_r_square_change <- round(hr_stress_m3_r - hr_stress_m2_r,2)

#Hindrance-Resource-Engagement

# b weights
hind.2.eng <- round(summary(hr_eng_m2)$coefficients[2, 1],2)
res.2hr.eng <- round(summary(hr_eng_m2)$coefficients[3, 1],2)

int.hr.3.eng <- round(summary(hr_eng_m3)$coefficients[4, 1],2)

#r squared
hr_eng_m2_r <- round(summary(hr_eng_m2)$r.squared,2)
hr_eng_m3_r <- round(summary(hr_eng_m3)$r.squared,2)

## R square change
hr_eng_anova <- anova(hr_eng_m2, hr_eng_m3)
hr_eng_r_square_change <- round(hr_eng_m3_r - hr_eng_m2_r,2)
```

```{r, results='asis'}
#I'm not touching this script - using it as a model and making two new chunks
library(kableExtra)

DV <- c("Burnout","","")
Step <- c("1", "","2")
Model <- c("Challenge", "Resource", "Challenge X Resource")
b <- c(chal.2.burn,res.2.burn,int.cr.3.burn)
DeltaR <- c("",paste(cr_burn_m2_r,"**"),cr_burn_r_square_change)

@@

DV <- c("Engagement","","", "Stress","","", "Burnout","","")
Step <- c("1", "","2", "1", "","2", "1", "","2")
Model <- c("Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource")
b <- c(chal.2.eng, res.2.eng, int.cr.3.eng, chal.2.stress, res.2.stress, int.cr.3.stress, chal.2.burn, res.2.burn, int.cr.3.burn)
R2 <- c("", cr_eng_m2_r, cr_eng_m3_r, "", cr_stress_m2_r, cr_stress_m3_r, "", cr_burn_m2_r, cr_burn_m3_r)
DeltaR <- c("",paste(cr_eng_m2_r),cr_eng_r_square_change, "",paste(cr_stress_m2_r),cr_stress_r_square_change, "",paste(cr_burn_m2_r),cr_burn_r_square_change)

regtable <- cbind(DV, Step, Model, b, R2, DeltaR)

@@

DV <- c("Engagement","","", "Stress","","", "Burnout","","")
Step <- c("1", "","2", "1", "","2", "1", "","2")
Model <- c("Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource")
b <- c(hind.2.eng, res.2hr.eng, int.hr.3.eng, hind.2.stress, res.2hr.stress, int.hr.3.stress, hind.2.burn, res.2hr.burn, int.hr.3.burn)
R2 <- c("", hr_eng_m2_r, hr_eng_m3_r, "", hr_stress_m2_r, hr_stress_m3_r, "", hr_burn_m2_r, hr_burn_m3_r)
DeltaR <- c("",paste(hr_eng_m2_r,"**"),hr_eng_r_square_change, "",paste(hr_stress_m2_r,"**"),hr_stress_r_square_change, "",paste(hr_burn_m2_r,"**"),hr_burn_r_square_change)

regtable <- cbind(DV, Step, Model, b, R2, DeltaR)

papaja::apa_table(regtable)
# How to get delta symbol and superscript
#https://cran.r-project.org/web/packages/reporter/vignettes/reporter-super.html#:~:text=To%20get%20superscripts%20or%20subscripts,to%20the%20desired%20cell%20value.
